\begin{abstract}
%------------------------------------------------------------------------------------------

This paper consists of the design, creation and development of a circular differential drive SLAM robot. The robot was equipped with two motorized wheels and two spherical wheels to stabilize the platform. The odometry sensors employed were two wheel encoders and a 6-DOF IMU. A 2D LIDAR was used to measure the surrounding. ROS2 was used for communication and interaction between different parts of the system, with SLAM Toolbox and Navigation2 integrated to perform SLAM and path planning. The system was evaluated and tested in both simulation and in real-world deployment, yielding promising SLAM results in small environments. Yet revisions and additional development is necessary to achieve a system with the desired capabilities. 

%------------------------------------------------------------------------------------------
\end{abstract}
%------------------------------------------------------------------------------------------


%------------------------------------------------------------------------------------------
\begin{comment}
    The abstract must be a concise yet comprehensive reflection of what is in your article. In particular, the abstract must be self-contained, without abbreviations, footnotes, or references. It should be a microcosm of the full article. The abstract must be between 150--250 words.
    
    An abstract should summarize the work in brief. 
\end{comment}
%------------------------------------------------------------------------------------------